\section{Syllabus}
\vspace{-0.5\onelineskip}
\begin{itemize}[nosep]
    \item{Read it!}
    \item Google Classroom codes, tutorials, late work policies... It's all there!
    \item We'll go through it together.
    \item{Put it in your notebook!}
\end{itemize}

\myProblems[Answer these questions about the syllabus]
{
    Where do you find our Google Classroom code? What is it?
}
{
    When are Mr. Hasan's tutorials?
}
{0.5in}



\section{Rules}
\vspace{-0.5\onelineskip}
\begin{itemize}[nosep]
    \item{Show up.}
    \item Work hard.
    \item Be nice.
\end{itemize}

Check out the posters for examples of what these mean.

\myProblems[Answer these questions about the class rules]
{
    You should speak like \myEmph{who} is in the room?
    What does that mean?
}
{
    Give two examples of what the rule \myEmph{Show Up} means.
}
{0.5in}



\section{Procedures}
These are the things we'll do {\itshape over and over} during the year.
\vspace{-0.5\onelineskip}
\begin{itemize}[nosep]
    \item{Attention Signal}
    \item Folders
    \item Food \& Drinks
    \item Passes \& Bathroom Break 
    \item Phones 
    \item Popsicle Sticks
    \item Turning in Work
\end{itemize}

\myProblems[Answer these questions about the class procedures]
{
    What do you have to give Mr. Hasan before he will give you a bathroom pass?
}
{
    What does Mr.~Hasan use popsicle sticks for?
}
{0.75in}

\vfill
\begin{tcolorbox}[center, width=5.25in]
    At the end of class, insert these handouts into your Algebra 2 folder:
    \vspace{-0.5\onelineskip}
    \begin{enumerate}[nosep]
        \item two (2) \myEmph{Table of Contents} pages 
        \item the \myEmph{Syllabus}
        \item the \myEmph{Rules}
        \item the \myEmph{Procedures}
        \item Today's \myEmph{Lesson 0.1} notes
    \end{enumerate}
    %
    \vspace{0.5\onelineskip}
    Write \myEmph{one line} in the table of contents for today.
\end{tcolorbox}
\vfill