\documentclass[12pt,letterpaper]{memoir}

\input{../../../common/packages}
\input{../../../common/defs}
\input{../../../common/scaffold}
\input{../../../common/assignment-defs}
\input{../../../common/system-table}
\input{../../../common/student-or-teacher}
\input{../../../common/graphs}
\input{../../../common/problems}
\input{../../../common/course-name}

\input{for-whom}
\iftstu 
    \dashundergapssetup{gap-font={\ECFAugie\MTversion{augie}\color{red}},}
\fi

% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*} % leave space in left margin for punched holes


\begin{document}
\pagestyle{plain}
\checkandfixthelayout
\raggedbottom


\noindent
%-----------------------------------------------------------------------------------------
\myAssignmentHeader{7.2}{Desmos Marbleslide Activity}
%-----------------------------------------------------------------------------------------

This Desmos activity is called a ``marbleslide'' for obvious reasons. 
For this assignment, go through the screens of the activity and answer the following 
questions.

\vspace{1\onelineskip}

\myProblems[Screen 2]
{
    Describe what happened when you clicked {\sffamily Launch}.
}
{
    What is the purpose of the blue curves?
}
{1in}


\myProblemsWithContent[Screen 3]
{
    The function $f$ started out as $f(x) = b^{x-h}$. 
    What were the starting values of $b$ and $h$?
    \tcblower
    \begin{itemize}[nosep]
        \item $b = $ \gap{999}
        \item $h = $ \gap{999}
    \end{itemize}
}
{
    What did you change $b$ and $h$ to?
    \tcblower
    \begin{itemize}[nosep]
        \item $b = $ \gap{999}
        \item $h = $ \gap{999}
    \end{itemize}
}

\myProblems[Screen 5]
{
    Desmos defines the domain as an expression in curly braces.
    You {\itshape had} to change the domain on this screen. 
    Why?
}
{
    Besides the change to the domain, 
    what transformation allowed you to roll over all the stars?
}
{1in}

\myProblems[Screen 6]
{
    The function $f$ started out as exponential {\itshape growth}, 
    but it grew too fast. 
    Is the function that you ended up with ``growth'' or ``decay''?
}
{
    You should have changed the base for function $f$.
    What was the value of the base that you ended up with?
}
{1in}

\myProblems[Screen 7]
{
    What kind of function do you need  
    for the marbles to roll over all the stars on this screen, 
    {\itshape growth} or {\itshape decay}?
}
{
    Describe all the changes you made to the function
    so that the marbles rolled over all the stars.
}
{1in}

\myProblems[Screens 9 \& 11]
{
    What kind of transformation do you get 
    when you change $-3$ to $+3$ on Screen 9?
}
{
    What kind of transformation do you get 
    when you change $-4$ to $+4$ on Screen 1?
}
{1in}

\myProblems[Screens 12 \& 13]
{
    Describe how the graph changes 
    when you change the base from $2$ to $1.2$.
    Is that a switch from {\itshape growth} to {\itshape decay}?
}
{
    What kind of change would you have to make 
    to the base to change it from {\itshape growth} 
    to {\itshape decay}? 
    (You may experiment on Screen 13 if you need to.)
}
{1in}

\myProblems[Screens 14 \& 15]
{
    Describe your strategy for changing the function. 
    What did you change, and why?
}
{
    Did it work?
}
{1in}

\myProblems[Screen 17]
{
    How many functions did you end up with on Screen 17?
}
{
    Describe your strategy on Screen 17.
}
{1in}

\myProblems[Screen 18]
{
    Is it true that you {\itshape must} have a domain modifier 
    (the curly braces) 
    on at least one function for Screen 18? 
    Why?
}
{
    How many functions did you use on Screen 18? 
    Do you think that's the fewest needed?
}
{1in}


\myProblems[Screen 21]
{
    When I first create Screen 21, 
    I thought that it might be impossible.
    Why do you think I thought that?
}
{
    I was wrong. Screen 21 is not impossible. 
    Describe how you solved it.
}
{1in}

\myProblems[Screen 23]
{
    How many functions did you use for Screen 23?
}
{
    Do you think Screen 23 is possible with just 
    {\itshape one function}? 
    Explain why or why not.
}
{1in}

\end{document}