\documentclass[10pt,letterpaper]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{0.75in}{*}{*}
\setlrmarginsandblock{0.75in}{*}{*}

\input{../../common/packages}
\input{../../common/head-foot}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.75em}

\begin{document}
\pagestyle{plain}
\checkandfixthelayout
\raggedbottom

\input{../../common/defs}

{\small Algebra 2}\hfill Name: \rule{2in}{0.15mm}

{\bfseries\Large In-Class 4.4 Matrix Applications}\hfill Period: \rule{0.5in}{0.15mm}

{\itshape
For the following word problems, formulate a system of linear equations,
and solve them using the Desmos matrix calculator at
} 
{\bfseries\ttfamily desmos.com/matrix}.
\vspace{1.5em}




{\bfseries\large 1)} 
You find a jar of dimes and quarters.
There is a total of 70 coins in the jar.
When you take them to the bank (to the coin counting machine),
you find that they added up to \$13.00.
How many dimes and how many quarters were in the jar?

\myWideMatrixTable[-0.1in]
\vspace{0.5in}
\hfill{\itshape (Ans: 30 dimes, 40 quarters)}
\vspace{2em}




{\bfseries\large 2)} 
You find another jar of 120 pennies, nickles and dimes.
You just happen to know that 
the number of nickles is equal to the number of dimes minus 10.
When you take them to the bank (to the coin counting machine),
you find that they added up to \$6.00.
How many pennies, nickles, and dimes were in the jar?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: 50 pennies, 30 nickles, 40 dimes)}
\vspace{2em}



\newpage
{\bfseries\large 3)} 
Arly's Game Arcade uses three different kinds of tokens for their game machines.
There are gold tokens.
There are silver tokens.
There are bronze tokens.
For \$20.00, you can buy any of the following mixes of tokens:
\begin{itemize}[itemsep=0in]
    \item 14 gold, 20 silver, 24 bronze
    \item 20 gold, 15 silver, 19 bronze
    \item 30 gold, 5 silver, 13 bronze.
\end{itemize}
How much does each kind of token cost?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: gold: \$0.50, silver: \$0.35, bronze: \$0.25)}
\vspace{2em}





{\bfseries\large 4)} 
Last weekend, the Nostream Movie Theater sold a total of 8500 movie tickets.
They earned \$64,600.00.
Tickets are sold in one of three ways:
\begin{itemize}
    \item A matinee (early show) ticket costs \$5.00.
    \item A student all-day ticket costs \$6.00.
    \item Regular tickets cost \$8.50.
\end{itemize}
They sold twice as many student tickets as matinee tickets.
How many of teach kind of ticket did they sell?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: 900 matinee, 1800 student, 5800 regular)}
\vspace{2em}




\newpage
{\bfseries\large 5)} 
Rudy's Ripoff Tienda sells hats, T-shirts, and jackets. 
You know the following three facts:
\begin{itemize}[itemsep=0in]
    \item 3 hats, 2 T-shirts, and 1 jacket cost \$140.00.
    \item 2 hats, 2 T-shirts, and 2 jackets cost \$170.00.
    \item 1 hat, 3 T-shirts, and 2 jackets cost \$180.00.
\end{itemize}
What is the cost of each of these three items?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: hat: \$15.00, T-shirt: \$25.00, jacket: \$45.00)}
\vspace{2em}



{\bfseries\large 6)} 
Guadalupe, Jennifer, and Karla work at Notear Jeans Company.
One day, the three of them sold a combined \$1480.00 worth of jeans.
Guadalupe sold \$120.00 more than Jennifer.
Jennifer and Karla together sold \$280.00 more than Guadalupe.
How much did each of them sell?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: Guadalupe: \$600.00, Jennifer: \$480.00, Karla: \$400.00)}
\vspace{2em}



\newpage
{\bfseries\large 7)} 
Max, Jonathan, and Kevin work at Topnotch Boot Company.
One day, the three of them sold a combined \$1550.00 worth of boots.
Guadalupe sold \$150.00 more than Jonathan.
Kevin sold \$250.00 less than Max.
How much did each of them sell?

\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: Max: \$650.00, Jonathan: \$500.00, Karla: \$400.00)}
\vspace{2em}





{\bfseries\large 8)} 
Juanita is buying fruit at the Fructose Fruit Market.
One week, she pays \$3.70 for 1 orange, 2 grapefruit, and 3 pears.
Another week, she pays \$8.09 for 5 oranges, 6 grapefruit, and 2 pears.
On the last week, she pays \$2.12 for 2 oranges, NO grapefruit, and 2 pears.
Find the price per orange, price per grapefruit, and price per pear.


\myWideMatrixTable[-0.1in]

\vspace{0.5in}
\hfill{\itshape (Ans: oranges: \$0.49 each, grapefruit: \$0.75 each, pears: \$0.57 each)}
\vspace{2em}


\end{document}