\documentclass[fleqn,letterpaper,12pt,printwatermark=false]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*}
% put "extra" vertical space at the bottom of a page
\raggedbottom 

\input{../defs/standard-packages}
\begin{document}

\newcommand{\myClassName}{Pre-AP Algebra 2}
\newcommand{\myUnitNumber}{1}
\newcommand{\myUnitTitle}{Introduction to Functions}
\newcommand{\myLessonNumber}{4}
\newcommand{\myLessonTitle}{Evaluating Expressions and Functions}


\input{../defs/guided-notes-defs}
\pagestyle{myPagestyle}

\checkandfixthelayout
\setlist{labelindent=\parindent,leftmargin=*,itemsep=0.025em,label=$\circ$}

% ---------------------HEADER------------------------------
\begin{myNotesHeader}
    \item \myCognitiveVerb{simplify} expressions using the \emph{order of operations}
    \item \myCognitiveVerb{evaluate} expressions given the value of all the variables
    \item \myCognitiveVerb{evaluate} a function given the value of its input variable
\end{myNotesHeader}

\begin{myVocabulary}
    \myVocabularyWord{operation}
    {
        some kind of mathematical calculation
        ($+$, $-$, multiply, $\sqrt{\,\,}$, etc...)

    }
    \myVocabularyWord{expression}
    {
        numbers and variables combined using various \emph{operations}
    }
    \myVocabularyWord{order of operations}
    {
        which operations should be done before the others
    }
    \myVocabularyWord{evaluate}
    {
        apply the \emph{order of operations} 
        to an expression to get a \myEmph{number}
    }
    \myVocabularyWord{simplify}
    {
        apply \emph{order of operations} 
        to an expression to get a \myEmph{simpler expression}
    }
\end{myVocabulary}

% ---------------------LESSON 1------------------------------
\begin{myLesson}[][]
    You learned the \emph{order of operations} in Algebra 1.
    It's often called PEMDAS or GEMDAS.
\end{myLesson}

% ---------------------CONCEPT 1------------------------------
\begin{myKeyConcepts}[To apply the order of operations\dots]
    Follow these GEMDAS steps in this order:
    \setlist{labelindent=\parindent,}
    \begin{enumerate}
        \item {\Large\slshape G:} simplify \myEmph{grouping} symbols (), [], \{\} 
        \item {\Large\slshape E:} simplify terms that have \myEmph{exponents}
        \item {\Large\slshape MD:} apply \myEmph{multiplication and division} going from \emph{left to right}
        \item {\Large\slshape AS:} apply \myEmph{addition and subtraction} going from \emph{left to right}
    \end{enumerate}
    The words \emph{evaluate} and \emph{simplify} are confusing. 
    They mean almost the same thing.
    I use the word ``evaluate'' when you should end up with a \myEmph{number} after you apply the order of operations.
    I use the word ``simplify'' when you should end up with a \myEmph{number} after you apply the order of operations.
\end{myKeyConcepts}

\myExample{
    Evaluate this expression:
    \(
        2 + 3\cdot5^2
    \)
}{1.25in}

\myExample{
    Evaluate this expression:
    \(
        16 - 3(8-3)^2 + 9
    \)
}{1.5in}

\myExample{
    Simplify this expression:
    \(
        2 + 3(x-2)^2
    \)
}{1.25in}

\myExample{
    Simplify this expression:
    \(
        16 - 3(2x-1)^2 + 9
    \)
}{1.5in}

In those examples
when we were asked to \emph{evaluate} expressions,
the expressions were just numbers, 
so it was obvious that results were numbers.
And 
when we were asked to \emph{simplify} expressions,
since we didn't know the value of $x$ ,
it was obvious that results were expressions.

However, some problems might ask you to \emph{evaluate} and expression
with variables in it 
by telling you the values of all the variables.
Again, the word ``evaluate'' is a hint to you that your answer should be a \myEmph{number}.

\myExample{
    Evaluate this expression:
    \(
        16 - 3(2x-1)^2 + 9
    \),
    where $x=2$.
}{1.5in}

\myExample{
    Evaluate this expression:
    \(
        1 - \sqrt{b^2 - 4ac}
    \),
    where $a=-1$, $b=4$, $c=-3$.
}{2in}


% ---------------------LESSON 2------------------------------
\begin{myLesson}[][]
    \emph{Function notation}
    is how we write down a function on paper.
    It is a precise way to specify
    \begin{itemize}
        \item the \myEmph{name} of the function,
        \item the \myEmph{rule} that tells you how to calculate the output of the function,
        \item the names of the \myEmph{input variable}, which is often $x$.
    \end{itemize}

    \begin{myLessonBox}
    The most common notation is $f(x)$.
    This tells you that the function is named $f$ 
    and that the name of the input variable is $x$.
    But it's missing the rule; 
    it does not tell us how to calculate the output.

    To fully specify a function, including the rule, we write $f(x) = \cdots$,
    where the stuff on the right is an algebraic expression involving $x$.
    That expression tells you how to calculate the output of the function.
    \end{myLessonBox}

    In math,
    function names are usually (but not always\footnote{
        An example of a function name that is not one letter 
        is $log(x)$, which we will study later in the year.
        In pre-calculus, you will use trigonometric functions,
        $sin(x)$ and $cos(x)$.
        In the software world, function and variable names almost always 
        are words that describe what they do, for example,
        \texttt{send\_email(my\_message)}.
    }) a single letter,
    and the input variable is often (but not always) $x$.
    for example, $f(x)$, $g(z)$, $v(t)$.

\end{myLesson}

% ---------------------CONCEPT 2------------------------------
\begin{myKeyConcepts}[To evaluate a function given the value of its input variable\dots]
    Follow these steps:
    \setlist{labelindent=\parindent,}
    \begin{enumerate}
        \item \myEmph{Substitute} the value of the input variable whereever it appears in the rule.
    \end{enumerate}
    The words \emph{evaluate} and \emph{simplify} are confusing. 
    They mean almost the same thing.
    I use the word ``evaluate'' when you should end up with a \myEmph{number} after you apply the order of operations.
    I use the word ``simplify'' when you should end up with a \myEmph{number} after you apply the order of operations.
\end{myKeyConcepts}

\myExample{
    Given the function
    \(
        f(x) = 3x-5
    \)
    evaluate $f(4)$.
}{1in}

\myExample{
    Given the function
    \(
        g(z) = 3z^2 - 2z + 1
    \)
    evaluate $g(-3)$.
}{1.5in}

\myExample{
    Given the function
    \(
        v(t) = \frac{1}{2}t^2 + 4t + 3
    \)
    evaluate $f(-4)$.
}{2.75in}

% \begin{myProblems2}%
%     {Factor the following monomials into prime factors.}%
%     {2in}%
%     %
%     {\( 32x^2 \)}
%     {\( 8 x^3y^2z \)}
% \end{myProblems2}
  


\end{document}