\whenTEACHER{
    \tiny
    This next problem is the one we said we can't calculate. 
    The Change of Base Formula lets us find it.
}

\myProblems[Find these logarithms using a calculator and the change of base formula. Round your answers to three digits after the decimal point.]
{
    $log_5(13)$  
    \whenTEACHER{
        \hfill\small 
        $
        \frac {log_{10}(13)} {log_{10}(5)} 
        \sim 
        \frac {log(13)} {log(5)} 
        \sim 
    1.5937
        $
    }
}
{
    $log_2(123)$  
    \whenTEACHER{
        \hfill\small 
        $
        \frac {log_e(123)} {log_e(2)} 
        \sim 
        \frac {ln(123)} {ln(2)} 
        \sim 
        6.9425
        $
    }
}
{0.25in}

\whenTEACHER{
    \tiny 
    You can see I chose to use COMMON LOG in one of those problems 
    and NATURAL LOG in the other. 
    I do that just to emphasize that either one works fine.
    In fact, FOR DIFFERENTIATION (!) you could quickly show them 
    on either/both problems that using log or ln gives you the SAME RESULT. 
    The interested kids seem to find this interesting.
}

\whenTEACHER{
    \tiny
    I STRONGLY encourage the students to write MORE than just the final answer,
    since it is VERY COMMON for students to make minor mistakes using logs on the calculator.
    I encourage them to write out their ``reasoning'' in how their applying the 
    formula as I do in the notes so that I can give them partial credit 
    if they make a silly mistake.
}

\whenTEACHER{
    \tiny 
    FINALLY, here's a trick to remembering the formula. 
    The kids think the formula is a hassle since there's logarithm soup. 
    But... it's NOT THAT BAD, I tell them. 
    Here's how to remember it (even if you have it in your notes)\\[0.5\onelineskip]
    Write $log_2(123)$ on the whiteboard and then ask which of the nubmers 2 and 123 
    is ``higher'' than the other as written on the whiteboard? 
    Well, 123 is higher, since 2 is the base written as a subscript. 
    So log(123) goes on TOP of the fraction in the formula, 
    and log(2) goes on the bottom.
}