\documentclass[12pt,letterpaper]{memoir}

\input{../../../common/packages}
\input{../../../common/defs}
\input{../../../common/scaffold}
\input{../../../common/assignment-defs}
\input{../../../common/system-table}
\input{../../../common/student-or-teacher}
\input{../../../common/graphs}
\input{../../../common/problems}
\input{../../../common/course-name}

\input{for-whom}
\iftstu 
    \dashundergapssetup{gap-font={\ECFAugie\MTversion{augie}\color{red}},}
\fi

% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*} % leave space in left margin for punched holes


\begin{document}
\pagestyle{plain}
\checkandfixthelayout
\raggedbottom


\noindent
\myAssignmentHeader{5.3}{The Absolute Value Parent Function}


%
%-----------------------------------------------------------------------------------------
%
\myProblemsWithContent
{
    Draw a \myEmph{big dot} for each of these points. 
    Then draw a \myEmph{dashed line} going through all of them.
    \begin{itemize}[nosep]
        \item $(2,-4)$
        \item $(2,2)$
        \item $(2,5)$
        \item $(2,-6)$
    \end{itemize}
    \vspace{-3\onelineskip}
    \hfill
    \begin{myTikzpictureGrid}{0.35} {6}{6}
        \whenTEACHER{
            \draw [ultra thick, dashed] (2.1,-7) -- (2.1,7);
            \draw[fill,red] (2,-4) circle (3mm);
            \draw[fill,red] (2,2) circle (3mm);
            \draw[fill,red] (2,4) circle (3mm);
            \draw[fill,red] (2,-6) circle (3mm);
            \node[draw,red,fill=white] at (5,8) {$x=2$};
        }
    \end{myTikzpictureGrid}
}
{
    Answer these questions about problem \#1. 
    \tcblower 
    \begin{itemize}[fullwidth]
        \item[] What are the $x$ coordinates of the points? 
        \item[] $x =$\gap{2}\\
        \item[] What is the \myEmph{equation} of the line? 
        \item[] $x =$\gap{2}\\
        \item[] Is the line horizontal or vertical?
        \item[] \gap{vertical}
    \end{itemize}
}

%
%-----------------------------------------------------------------------------------------
%
\myWideProblemWithContent
{
    In this graph, I've sketched the \myEmph{vertex} 
    of the absolute value parent function and two other points on it.
    Add the following things to the graph:
    \begin{enumerate}[nosep]
        \item At least four other points on the function.
            (Hint: Look at the \myEmph{Lesson 5.3} notes.)
        \item Draw the graph of the partent function. 
            (Make sure it goes through all the points.)
        \item Draw the \myEmph{axis of symmetry}.
            (Hint: It's the \myEmph{vertical line} going through the vertex.)
    \end{enumerate}
    %
    \begin{center}
    \begin{myTikzpictureGrid}{0.7} {5}{5}
        \draw[fill=black,draw=black,ultra thick] (0,0) circle (2mm);
        \draw[fill=black,draw=black] (3,3) circle (1.5mm);
        \draw[fill=black,draw=black] (-3,3) circle (1.5mm);
        \whenTEACHER{
            \draw[fill=red,draw=red] (1,1) circle (1.5mm);
            \draw[fill=red,draw=red] (-1,1) circle (1.5mm);
            \draw[fill=red,draw=red] (5,5) circle (1.5mm);
            \draw[fill=red,draw=red] (-5,5) circle (1.5mm);
            %
            \draw [ultra thick, dashed] (0.1,-6) -- (0.1,6);
            %
            \tkzFct[ solid, ultra thick, samples=100, domain=-5:0,]{-x}
            \tkzFct[ solid, ultra thick, samples=100, domain=0:5,]{x}
        }
    \end{myTikzpictureGrid}
    \end{center}
}

\myProblems 
{
    What are the \myEmph{coordinates} of the vertex?
}
{
    What is the \myEmph{equation} of the axis of symmetry? 
}
{0.25in}
[\myAnswer{$(0,0)$}]
[\myAnswer{$x=0$}]

\myProblems 
{
    Do the points on the graph have $y$-coordinates that are 
    greater or less than zero?
}
{
    What is the \myEmph{range} of the function?
}
{0.5in}

\myProblems
{
    Does the graph of the absolute parent function 
    \myEmph{open up} or \myEmph{open down}?
}
{
    Is the vertex a \myEmph{minimum} or a \myEmph{maximum}?
    EXPLAIN why you say that.
}
{1.5in}

\myProblems
{
    What is a ``parent function''? 
    (Hint: Look the vocabulary in the \myEmph{Lesson 5.3} notes.)
}
{
    There is one ``attribute'' that we discussed in the notes 
    that I have not asked you about here. What is the name that attribute?
    (Hint: Look at the notes!!)
}
{1.5in}

\myWideProblem{
    How would you describe the shape of the graph of the 
    absolute value parent function?
}
{2in}


\end{document}