\documentclass[letterpaper,12pt]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*}
% put "extra" vertical space at the bottom of a page
\raggedbottom 

\usepackage{amsmath}
\usepackage{xparse} % for NewDocumentCommand et al.
\usepackage{enumitem}
\usepackage{transparent} % for \transparent, which I use in the watermark
\usepackage[slantedGreek]{mathpazo} \usepackage{helvet} % use Palatino et al.
% \usepackage{booktabs} % prettier tables

\usepackage[]{xwatermark}
\newwatermark*[
    allpages,
    color=red!30,angle=45,
    scale=4,
    xpos=-10, ypos=0
]{%
    \transparent{0.4}dhasan example%
}

\usepackage{dashundergaps} % for \gap
\dashundergapssetup{
    teacher-mode=true, % set to true to show answers 
    gap-format=underline,
    teacher-gap-format=underline,
    gap-font={\sffamily},
    gap-numbers=true,
    gap-widen=true,
    gap-extend-percent=150, % note: making this too big might create errors
    gap-number-format=\,\textsuperscript{\normalfont(\thegapnumber)},
}

\usepackage{tcolorbox}
\tcbuselibrary{skins}
\tcbuselibrary{raster}

% ---------------------DOCUMENT------------------------------
\begin{document}
\input{../defs/guided-notes-defs}
\pagestyle{myPagestyle}

\checkandfixthelayout
\setlist{labelindent=\parindent,leftmargin=*,itemsep=0.025em,label=$\circ$}
% ---------------------Notes------------------------------
\begin{myNotesHeader}[Unit 5 : Quadratic Functions][5.5]{Factoring A GCF Out of a Polynomial}
    \item \myCognitiveVerb{factor} a monomial term into \emph{``prime'' factors}
    \item \myCognitiveVerb{find} the \emph{GCF} of several monomials
    \item \myCognitiveVerb{factor} the \emph{GCF} out of a polynomial
\end{myNotesHeader}
  
% ---------------------1------------------------------
\begin{myKeyConcepts}[To factor a monomial into its ``prime'' factors\dots]
    \setlist{labelindent=\parindent,leftmargin=*,itemsep=1em}
    \begin{enumerate}
        \item Factor the coefficient (number) into \myFillInBlank{prime factors}
        and write each of them down.
        \item Write each variable (letter) down a number of times equal to its 
        \myFillInBlank{exponent}.
    \end{enumerate}
\end{myKeyConcepts}

\myExample{
    Factor this monomial term into its prime factors: 
    \( 24 x^2yz^3 \)
}{1.5in}

\begin{myProblems2}%
    {Factor the following monomials into prime factors.}%
    {2in}%
    %
    {\( 32x^2 \)}
    {\( 8 x^3y^2z \)}
\end{myProblems2}
  
% ---------------------2------------------------------
\begin{myKeyConcepts}[To find the GCF of several monomials\dots]
    \setlist{labelindent=\parindent,leftmargin=*,itemsep=1em}
    \begin{enumerate}
        \item Factor \myFillInBlank{each term} into its prime factors.
        \item Write down \myFillInBlank{each prime factor} that occurs in every term. 
        If a prime factor occurs multiple times \emph{in every term}, 
        write it down that many times.
        \item \myFillInBlank{Multiply} all those prime factors together.
    \end{enumerate}
\end{myKeyConcepts}

\myExample{
    Find the GCF of the following monomials: 
    \( 24 x^2yz^3 \quad\text{and}\quad 8 xyz^2 \)
}{1.5in}

\begin{myProblems2}{Find the GCFs of the monomials shown.}{2in}
    {\( 9x^3 \quad\text{and}\quad 27x \)}
    {\( 12x^2y^2 \quad\text{and}\quad 2xy^2 \)}
\end{myProblems2}

  % ---------------------3------------------------------
\begin{myKeyConcepts}[To factor the GCF out of a polynomial\dots]
    \setlist{labelindent=\parindent,leftmargin=*,itemsep=1em}
    \begin{enumerate}
        \item Factor \myFillInBlank{each term} into its prime factors.
        \item Find the GCF of \myFillInBlank{all the terms} in the polynomial, 
        \item Factor that GCF out of each term and \myFillInBlank{write it in front}.
    \end{enumerate}
\end{myKeyConcepts}

\myExample{
    Find the GCF of the following polynomial: 
    \( 24 x^2yz^3 + 8 xyz^2 + 4xy \)
}{1.5in}

\begin{myProblems2}{Find the GCFs of the polynomials shown.}{2in}
    {\( 4x^3 + 12x \)}
    {\( 6x^3 + 3x^2 + 27x \)}
\end{myProblems2}

\end{document}