

\begin{myConceptSteps}{
    To solve a system of linear equations with matrices\dots
}
    \myStep{variables}{
        Determine what the unknown variables in the word problem are,
        and write them down.
    }
    \myStep{equations}{Write the system of equations.
        \begin{itemize}
            \item Figure out the \gap{equations} that come from the word problem.
            \item \gap{Reorder} them so the variables \gap{line up} 
            and the constant numbers are on the \gap{right}.
        \end{itemize}
    }
    \myStep{matrices}{
        Fill in \gap{$A$} and \gap{$B$}.
    }
    \myStep{solve}{
        Use the Desmos matrix \gap{calculator} 
        to calculate the solution as {\boldmath $A^{-1}B$}.
    }
\end{myConceptSteps}




\begin{myExample}{
    The price of a ticket at a small fair is 
    \$1.50 for children and 
    \$4.00 for adults. 
    On a certain day, we know two things:
    \begin{itemize}[itemsep=0in]
        \item 2200 people paid to enter the fair, and
        \item a total of \$5050.00 was earned from ticket sales.
    \end{itemize}  
    How many children and how many adults attended on that day?
        }
    \myWideMatrixTable
    \vspace{6em}
\end{myExample}

{\bfseries\itshape Warning:} I worded this problem to make the two equations {\itshape easy}
to see---they come from the two bullet items. You can't always depend on that.
It was just something to help get you started.
One of the skills in solving word problems is to ``break up'' the words on your own.
It's difficult to teach 
and just comes from experience.
So I'll give you some experience in the homework!

