\documentclass[10pt,letterpaper]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{1in}{*}{*}
\setlrmarginsandblock{1in}{*}{*}

\input{../../common/packages}
\input{../../common/head-foot}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.75em}

\begin{document}
\pagestyle{plain}
\checkandfixthelayout
% \raggedbottom
\dashundergapssetup{teacher-mode=false,}

\input{../../common/defs}

{\small Pre-AP Algebra 2}\hfill Name: \rule{2in}{0.15mm}

{\bfseries\Large PAP HW 4.4 (DAY 2) A Sneak Peak at Linear Regression}\hfill Period: \rule{0.5in}{0.15mm}



\begin{tcolorbox}
    \itshape\small
    Work this problem if you have finished yesterday's sheet of problems.
    This is a ``warm up'' to the topic of 
    {\bfseries\itshape linear regression}, which we will discuss tomorrow.
\end{tcolorbox}




\section*{Four equations \& four unknown variables} 
Here are four $x$-$y$ points:
\begin{center}\begin{tabular}{cc}
    \toprule
    $x$ & $y$ \\
    \midrule
    -5 & 5 \\
    0 & -2 \\
    3 & 2 \\
    5 & 0 \\
    \bottomrule
\end{tabular}\end{center}
Using what you learned a few days ago,
find the equation of the cubic  
\[
    y = a + bx + cx^2 + dx^3
\]
that goes through
those four points.
Remember,
\begin{itemize}[itemsep=0in]
    \item You have four unknown variables, $a$, $b$, $c$, $d$.
    \item By evaluating the cubic at the four points, you get four equations
    involving the four unknow variables.
    \item Using the {\scshape Desmos Matrix Calculator}, 
    you can calculate $A^{-1}B$ to find the unknown variables.
\end{itemize}
(You'll probably need some scratch paper.)\vspace{1em}

\begin{minipage}{2in}
    {\Large
    $a$ = \gap{\hspace{1em}}\\[1em]
    $b$ = \gap{\hspace{1em}}\\
    }
\end{minipage}
\begin{minipage}{2in}
    {\Large
    $c$ = \gap{\hspace{1em}}\\[1em]
    $d$ = \gap{\hspace{1em}}\\
    }
\end{minipage}
\hrule





\section*{Graph it!}
Enter that function into the {\scshape Desmos Graphing Calculator}.
Does the curve seem to pass exactly through the four points in the table?

Answer yes or no: \gap{\hspace{3em}}

Does the point $(2,1)$ seem to be ``near'' the graph of the cubic function?

Answer yes or no: \gap{\hspace{3em}}\vspace{1em}
\hrule





\section*{Five equations \& four unknown variables?} 
So let's consider {\bfseries\itshape five} $x$-$y$ points.
\begin{center}\begin{tabular}{cc}
    \toprule
    $x$ & $y$ \\
    \midrule
    -5 & 5 \\
    0 & -2 \\
    3 & 2 \\
    5 & 0 \\
    2 & 1 \\
    \bottomrule
\end{tabular}\end{center}

Using all {\bfseries\itshape five} of those points,
formulate {\bfseries\itshape five} equations 
and write out the new $A$ and $B$ matrices below:
\par
{\Large
    \vspace{3em}
    \hfill $A = $\hspace{1.5in} \hfill $B = $\hspace{1.5in} \hfill
    \vspace{3em}
}

Use the {\scshape Desmos Graphing Calculator}
to calculate $A^{-1}B$. 
What happens? Explain what you think is going on.
\vspace{2.5in}
\hrule


\section*{Sneak peak at linear regression}

In a web browser (Safari, Chrome... on your phone), go to this URL:\\
\url{https://www.desmos.com/calculator/nzz8zxtguy}.

The graph there has a table of the same five data points that you used, above.
And it uses something called 
{\bfseries\itshape linear regression}
to find a cubic equation passing through those points.

This is something the $A^{-1}B$ matrix math was unable to do
(as you found above).

Linear regression uses more complicated matrix math 
to do this. 
So in fact it {\bfseries\itshape is} possible. 
It's just that the curve won't go through all five points exactly.
Linear regression is a method for finding the ``best'' curve that 
passes through all the points.
To see this, 
play with the slider on the graph. It changes the
$y$-coordinate of that fifth point. 

As you slide the slider,
you should be able to see that the curve no longer passes through 
all the points exactly.
Yet, it is possible to prove that the curve is the best one
in the sense of being {\itshape as close as possible to all the points
at the same time.}

We will talk more about linear regression tomorrow.
\end{document}
