\documentclass[12pt,letterpaper]{memoir}

\input{../../../common/packages}
\input{../../../common/defs}
\input{../../../common/assignment-defs}
\input{../../../common/system-table}
\input{../../../common/student-or-teacher}
\input{../../../common/graphs}
\input{../../../common/problems}
\input{../../../common/course-name}

\input{for-whom}

% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*} % leave space in left margin for punched holes


\begin{document}
\pagestyle{plain}
\checkandfixthelayout
\raggedbottom


\noindent
\myAssignmentHeader{word problems for U1T2}{A}

%

%
%-----------------------------------------------------------------------------------------

{
    \vfill 
    
    Karla, Jan and Dan went shopping for Halloween treats.
    \begin{itemize}[nosep]
        \item Karla bought 3 chocolate pumpkins, 4 masks and 8 candy witches. 
        He spent \$36.65.
        \item Jan bought 5 chocolate pumpkins, 3 masks and 10 candy witches. 
        He spent \$37.50.
        \item Dan bought 4 chocolate pumpkins, 5 masks and 6 candy witches. 
        He spent \$43.45.
    \end{itemize}  
    \vspace{1\onelineskip}
    How much does each kind of treat cost? 
    (\myEmph{Show your work} by filling in the table below.)
    %
    \mySystemTable[7]
    \small
    a chocolate pumpkin: \$\gap{2.55}
    \hfill 
    a mask: \$\gap{5.75}
    \hfill 
    a chocolate witch: \$\gap{0.75}

%
%-----------------------------------------------------------------------------------------
%
\vfill 

Kiki, Jonathan and Benita went shopping for Halloween treats.
\begin{itemize}[nosep]
    \item Kiki bought 3 red hots, 4 masks and 10 candy ghosts. 
    He spent \$39.35.
    \item Jonathan bought 5 red hots, 3 masks and 6 candy ghosts. 
    He spent \$35.05.
    \item Benita bought 4 red hots, 5 masks and 6 candy ghosts. 
    He spent \$44.60.
\end{itemize}  
\vspace{1\onelineskip}
How much does each kind of candy cost? 
(\myEmph{Show your work} by filling in the table below.)
%
\mySystemTable[7]
\small
a red hot: \$\gap{2.45}
\hfill 
a mask: \$\gap{6.00}
\hfill 
a candy ghost: \$\gap{0.80}

\vfill


\end{document}