\newpage
In science,
we often want to solve a formula for one of the variables
{\bfseries\itshape without} knowing the value of the other variables.
This freaks algebra students out. 
It shouldn't. 
Here's why.

Suppose I give you a formula like $F = 2a + 3b$.
And then I tell you to solve it for $b$ given $F=1000$ and $a=10$.
You could do that using what you just learned above.
But then I change my mind and say $F=2000$ and $a=25$.
You could do it again doing almose the same thing, just with different numbers.
But then I change my mind again and say $F=900$ and $a=2.1$.
You could do it yet again. And again. And again.

Eventually you'll get tired of this game\footnote{
    Don't believe me? Come see me sometime later in the year, and I'll give you 
    an assignment of solving $F = ma$ for $a$ one hundred times for the different values of $F$ and $m$ like these:
    \begin{align*}
        100 &= 2a\\
        101 &= 2.5a\\
        103.2 &= 6.8a\\
        121 &= 52a\\
        1234 &= 89a
    \end{align*}
},
since each time I change my mind, you'd end up doing the exact same thing 
just with different numbers.
How many times to you have to do it, before you ask, ``Isn't there a better way?''
There is a better way: {\bfseries\itshape solve the formula first}, before you plug in numbers.

\begin{myConceptSteps}{To solve a formula for one variable in terms of all the other variables\dots}
    \myStep{rewrite}{
        Rewrite the equation so that you get the one variable by itself.
        This process is very similar to you you solve the equation,
        but when you apply inverse operations, you will be doing algebra instead of arithmetic.
    }
\end{myConceptSteps}


\myBlankExample{2.75in}{
    Solve the perimeter equation for $h$:
    \[
        P = 2h + 2w
    \]
}

\myBlankExample{2in}{
    Einstein's relativity equation is, $E = mc^2$.
    Solve this formula for $m$.
}


\begin{taggedblock}{on-level}
    \myBlankExample{2in}{
        Solve this formula for $b$: 
        \[
            Q = 5a^2 + 2b -c
        \]
    }
    \end{taggedblock}
\begin{taggedblock}{pre-AP}
    \myBlankExample{2in}{
        Solve this formula for $b$: 
        \[
            2Q = 5a^2 + 2ab - 13c
        \]
    }
    \end{taggedblock}

