\myProblemsWithContent[%
For the following pairs of variables, 
tell whether you would expect them to have 
a positive linear correlation, a negative linear correlation, or no linear correlation. 
Would the correlation (if any) be relatively strong or weak?
Explain your reasoning.
]
{
    \footnotesize
    \begin{itemize}[nosep,fullwidth]
        \item weight vs. blood pressure\vspace{1.5\onelineskip}
        \item math SAT scores vs. Algebra 2 grades\vspace{1.5\onelineskip}
        \item years smoking vs. lung capacity \vspace{1.5\onelineskip}
        \item hours per day on phone vs. height\vspace{1.5\onelineskip}
    \end{itemize}
}
{
    \footnotesize
    \begin{itemize}[nosep,fullwidth]
        \item GPA vs. number of siblings\vspace{1.5\onelineskip}
        \item foot size vs. weight\vspace{1.5\onelineskip}
        \item daily temperature vs. cost of a gallon of gas \vspace{1.5\onelineskip}
        \item speed limit vs. number of accidents \vspace{1.5\onelineskip}
    \end{itemize}
}

\myProblems[%
Use linear regression on the following data\footnote{
    U.S. Bureau of the Census, {\itshape Statistical Abstract of the United States: 1994}
} to answer these problems.\\
    \vspace{-1\onelineskip}
    \begin{center}
        \footnotesize
        \begin{tabular}{cc}
            \toprule 
            year ($x$) & \% smokers among 18--25 year olds ($y$) \\
            \midrule 
            1974 & 48.8 \\
            1979 & 42.6 \\ 
            1985 & 36.8 \\ 
            1988 & 35.2 \\ 
            1992 & 31.9 \\
            \bottomrule
        \end{tabular}
    \end{center}
]
{
    \small 
    Find the equation of the {\itshape line of best fit} 
    and the {\itshape correlation coefficient, $r$}. Interpret $r$.
}
{
    \small
    Using your line of best fit, estimate the percent of 18--25 year olds who smoked in 1990.
    Since $1974<1990<1992$, this is called \myEmph{interpolation}.
}
{0.75in}

\myWideProblem
{
    \small
    Using your line of best fit, estimate the percent of 18--25 year olds who smoked in ten years from now.
    Do you believe the answer? Explain why or why not.\\[0.5\onelineskip]
    Since $2032$ is ``outside'' our dataset, this is called \myEmph{extrapolation}.
}
{1in}