\documentclass[12pt,letterpaper]{memoir}
    % memoir commands to define the text block geometry
    \setulmarginsandblock{1.25in}{*}{*}
    \setlrmarginsandblock{1.5in}{*}{*} % leave space in left margin for punched holes

\input{../../../common/packages}
    \dashundergapssetup{
        gap-format=underline,
        teacher-gap-format=dot,
        gap-font={\ECFAugie\MTversion{augie}\color{black}},
        gap-numbers=false,
        gap-widen=true,
        gap-extend-percent=75, % note: making this too big might create errors
        gap-number-format=\,\textsuperscript{\normalfont(\thegapnumber)},
    }
\input{../../../common/defs}
\input{../../../common/graphs}
\input{../../../common/problems}
\input{for-whom}


\begin{document}
\pagestyle{plain}
\checkandfixthelayout
\raggedbottom

\setlength{\parindent}{0in}
\setlength{\parskip}{\onelineskip}
\setsecnumdepth{subsection}

%-----------------------------------------------------------------------------------------
\chapter*{Mr. Kelly and Mr. Sullivan Go For a Walk}
%-----------------------------------------------------------------------------------------
This is my worked solution to the last 8.2 Test Prep problem. 
This was the one that I tried (quite unsuccessfully) to explain in class. 

\section{Given} 

Mr. Kelly and Mr. Sullivan are walking down a straight street.
For $0 \le t \le 20$,
Mr. Kelly's velocity at time $t$ is given by 
%
\begin{equation*}
    K(t) = 16500 (t^2 - 5t + 74.33)^{-1} 
\end{equation*}
%
and Mr. Sullivan's velocity is given by 
%
\begin{equation*}
    S(t) = 41 t^3 e^{-0.6t} 
\end{equation*}

We also know that:
\begin{itemize}[nosep]
    \item The units for distance are {\itshape yards}.
    \item The units for time are {\itshape minutes}.
    \item Both velocities are {\itshape positive} for $0 \le t \le 20$.
    \item Mr. Kelly is 5 yards ahead of Mr. Sullivan at $t=0$.
    \item Mr. Kelly is {\itshape ahead} of Mr. Sullivan the whole time.
\end{itemize}
 
\section{To Do}
\begin{enumerate}[nosep]
    \item \myEmph{An integral.} Find the value of 
    $\frac{1}{5}  \int_{10}^{15}K(t)dt$. 
    Explain {\itshape what it means} in the context of this problem, including its units.
    %
    \item \myEmph{Speed up or slow down.} At $t=7$, is Mr. Kelly {\itshape speeding up} or {\itshape slowing down}? 
    %
    \item \myEmph{Separation increase or decrease.} Is their separation distance {\itshape increasing} or {\itshape decreasing} at $t=7$? 
    %
    \item \myEmph{Separation maximum.} What is the {\itshape maximum separation distance} between them during $0\le t\le20$?
\end{enumerate}



\section{How I used the TI-84} 

Here are some comments about how I used the TI-84.
\begin{itemize}[nosep]
    \item I entered $K(t)$ into $Y_1$ and $S(t)$ into $Y_2$.
    \item I did this because I wanted to use {\ttfamily[vars]} {\ttfamily[Y-vars]} {\ttfamily[Function]} a lot.
    \item I also entered $Y_1-Y_2$ into $Y_3$.
    \item I did this because it's the derivative of the {\itshape separation distance}.
\end{itemize}

I tried in class to show you how to use the TI-84 to find where 
the graphs of $K$ and $S$ intersect.
My problem was that I used {\ttfamily [ZoomFit]},
and the graphing window got messed up (with huge {\ttfamily X-min} and {\ttfamily X-max}).
By experimenting later, I was able to set the window limits to sensible values.
If you do not know how to do this, make sure to talk to me.





\section{Solution}

\subsection{An integral}

First, ignore the leading fraction. Just look at the integral.
It's the integral of a \myEmph{velocity} over a time interval.
That means it's the \myEmph{net displacement} during that time, i.e., $\Delta x$.
The interval of time happens to be five seconds long. 
So the leading fraction, $\frac{1}{5}$, is division by $\Delta t$. 
Therefore,

\begin{tcolorbox}[colback=white]
    $\frac{1}{5}  \int_{10}^{15}K(t)dt$ \! is $\frac{\Delta x}{\Delta t}$, 
    which is the {\itshape average velocity} over the interval.
\end{tcolorbox}



\subsection{Speed up or slow down}

A moving object is ``speeding up'' when 
its acceleration vector points in the same direction as its velocity vector.
In a one dimensional case like this, 
that means the {\itshape sign} of the two is the same.
On the other hand, 
a moving object is ``slowing down'' when 
the acceleration and velocity have different signs.

I used the TI-84 to calculate the velocity, $K(7)$, using 
{\ttfamily [2ND] [CALC] [value] } applied $Y_1$, which gave $K(7) \approx 186.8$, 
which is \myEmph{positive}.

I used the TI-84 to calculate the acceleration, $a(7) = K'(7)$, using 
{\ttfamily [MATH] [8]} applied to $Y_1$, which gave $K'(7) \approx -19.03$, 
which is \myEmph{negative}.


\begin{tcolorbox}[colback=white]
    Because these two signs are opposites, Mr. Kelly is \myEmph{slowing down} at $t=7$.
\end{tcolorbox}




\subsection{Separation increase or decrease} 

The separation distance is increasing or decreasing depending on whether its derivative 
is positive or negative. 

The derivative of the separation distance is $K(t) - S(t)$.
I evaluated this at $t=7$ using 
{\ttfamily [2ND] [CALC] [value]} applied to $Y_3$, which gave $K(7) - S(7) \approx -24.1$.
\begin{tcolorbox}[colback=white]
    Since this is negative, the separation distance between Mr. Kelly and Mr. Sullivan is \myEmph{decreasing} at $t=7$.
\end{tcolorbox}


\subsection{Separation maximum}

Remember, 
finding a maximum or minimum of a function on an interval requires evaluating the function at the
\begin{itemize}[nosep]
    \item {critical points} and 
    \item boundary points.
\end{itemize}
This is important, since any max/min values at the critical points  
might only be \myEmph{local} maxima or minima, 
and we are interested in the \myEmph{global} max/min values 
which can occur at the boundaries.

To start with, though, let's find the value of $t$ for the critical point(s).
We do this by setting the derivative of the sepration distance equal to zero:
\begin{equation*}
    K(t) - S(t) = 0
\end{equation*}
I did this on the TI-84 by using 
{\ttfamily [2ND] [CALC] [zero]} applied to $Y_3$. 
There are two zeros, which the calculator found as $t\approx 3.93$ and $t\approx 8.25$.

Knowing this, I evaluated the separation distance at these to critical points and also 
at the boundaries, $t=0$ and $t=20$.

The difficult thing in this problem 
is remembering how to calculate the separation distance.
(We have the separation velocity, not the distance!)

But wait! This is an application of {\itshape accumulation functions} 
to the separation distance.
\begin{align*}
    \text{\itshape sep. distance at time}\,\, T 
        &= \text{\itshape initial sep. distance} 
        + 
        \int_0^T (\text{\itshape sep. velocity}) dt \\ 
        &= 5 
        + \int_0^T (K(t) - S(t)) dt 
\end{align*}
And I evaluated that last expression four times using {\ttfamily [MATH] [9]} 
applied to $Y_3$.

\begin{center}
\begin{tabular}{c|c}
    \toprule
    $T$ & {\itshape sep. distance} \\ 
    \midrule
    $0$ & 5\\
    $3.93$ & 533\\ 
    $8.25$ & 429 \\ 
    $20$ & 960\\
    \bottomrule
\end{tabular}
\end{center}

Notice that (sure enough) the actual maximum is \myEmph{not} at one of the critical points,
which I worked so hard to find. 
It occurs on the final boundary at $t=20$. 
\begin{tcolorbox}[colback=white]
    The maximum separation distance between Mr. Kelly and Mr. Sullivan 
    occurs at the very end and is approximately 960 yards.
\end{tcolorbox}

\end{document}