\documentclass[fleqn,letterpaper,12pt,printwatermark=false]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*}
% put "extra" vertical space at the bottom of a page
\raggedbottom

% ---------------------DOCUMENT------------------------------
\input{../defs/standard-packages} 
\begin{document}

\newcommand{\myClassName}{Pre-AP Algebra 2}
\newcommand{\myUnitNumber}{1}
\newcommand{\myUnitTitle}{Introduction to Functions}
\newcommand{\myLessonNumber}{9}
\newcommand{\myLessonTitle}{Inverse Functions}


\input{../defs/guided-notes-defs} 
\pagestyle{myPagestyle}

\checkandfixthelayout
\setlist{labelindent=\parindent,leftmargin=*,itemsep=0.025em,label=$\circ$}

% ---------------------HEADER------------------------------
\begin{myNotesHeader}
    \item \myCognitiveVerb{find} the inverse of a function
\end{myNotesHeader}

\begin{myVocabulary}
    \myVocabularyWord{ordered pairs}{
            two numbers in parentheses, eg, $(4,-3)$
        }
        \myVocabularyWord{inverse functions}{
            two functions that ``undo'' each other
        }
        \myVocabularyWord{$f^{-1}$}
        {
            math notation for the inverse of $f$
        }
\end{myVocabulary}

% ---------------------LESSON------------------------------

\begin{myLesson} 
    Remember that one way a relation can be represented
    is as a set of ordered pairs that tell you
    which value of $x$ is associated with 
    which value of $y$.
    We can think of that as a \emph{mapping}
    from the inputs ($x$'s) to the outputs ($y$'s).
    For example the following relation 
    \[  
        \{ (1,5), (2,-3), (3,3) \}
    \]
    can be represented by the following mappings
    (one for each ordered pair)
    \begin{align*}
        1 &\Longrightarrow 5
        \text{
            \tiny\itshape\qquad
            \dots With 1 as input we get 5 as output.
            This is from the $(1,5)$ ordered pair.
        }\\
        %
        2 &\Longrightarrow -3
        \text{
            \tiny\itshape\quad
            \dots With 2 as input we get -3 as output.
            This is from the $(2,-3)$ ordered pair.
        } \\
        %
        3 &\Longrightarrow 3
        \text{
            \tiny\itshape\qquad
            \dots With 3 as input we get 3 as output.
            This is from the $(3,3)$ ordered pair.
        }
    \end{align*}

    Inverse relations answer the question, 
    ``How do we get back to the inputs if we know the outputs?''
    They {\bfseries\itshape turn the mapping around}.
    They ``undo'' what the relation did.
    They take you back to where you started.
    
    In the example above,
    the inverse mapping would be
    \begin{align*} 
        5 &\Longrightarrow 1
        \text{
            \tiny\itshape\quad
            \dots With 5 we get back to 1.
        }\\
        %
        -3 &\Longrightarrow 2
        \text{
            \tiny\itshape\quad
            \dots With -3 we get back to 2.
        } \\
        %
        3 &\Longrightarrow 3
        \text{
            \tiny\itshape\quad
            \dots With 3 we get back to 3.
        }
    \end{align*}
    And this is a new relation with the order of the numbers \emph{reversed}:
    \[  
        \{ (5,1), (-3,2), (3,3) \}
    \]
    %
    So, this is what you should remember.
    \begin{myLessonBox}
        Given a relation (or a function),
        you get the inverse by reversing (swapping, switching) 
        the order of the inputs and outputs.
        When the variables are $x$ and $y$, 
        this is {\bfseries\itshape swapping $x$ and $y$}.
    \end{myLessonBox}
\end{myLesson}

% ---------------------CONCEPT 1------------------------------
\begin{myKeyConcepts}[To find the inverse of a relation given as a bunch of points\dots]
    Follow these steps:
    \setlist{labelindent=\parindent,itemsep=0.4em}
    \begin{enumerate}
        \item Count the number of ordered pairs in the original relation.
        \item Write a \emph{new set} of empty ordered pairs with the 
        same number of pairs as the original relations.
        \item Fill in the empty ordered pairs in the new set
        by \emph{reversing the $x$ and $y$ values} in each of the
        original pairs.
    \end{enumerate}
    This new set of ordered pairs is the inverse relation.
\end{myKeyConcepts}

\myExample{
    Find the inverse of 
    \[ 
        \{
            (1,10), (2,8), (5,-3), (5,7)
        \}
    \]
}{0.75in}

\myExample{
    Find the inverse of 
    \[ 
        \{
            (2,10), (2,8), (2,0), (2,-1), (2,-4)
        \}
    \]
}{0.75in}

% ---------------------CONCEPT 2------------------------------
\begin{myKeyConcepts}[To find the inverse of a function specified by a rule, $f(x)$\dots]
    Follow these steps:
    \setlist{labelindent=\parindent,itemsep=0.4em}
    \begin{enumerate}
        \item \myEmph{Rewrite}the $f(x) = \cdots$ rule as $y=\cdots$.
        \item \myEmph{Swap} the $x$'s and $y$'s.
        Replace the original $y$ by $x$.
        Replace all of the original $x$'s by $y$.
        \item \myEmph{Solve}the new equation for $y$.
        \item {\bfseries\itshape Inverse Notation.}
        Replace the $y$ by $f^{-1}(x)$.
    \end{enumerate}
\end{myKeyConcepts}

\myExample{
    Find $f^{-1}$, the inverse of the function,
    \( f(x) = x-8 \).
}{4in}

\myExample{
    Find the inverse of 
    \( g(z) = 3z \).
    (Don't forget to write it as $g^{-1}(z) = \cdots$.)
}{4in}

\myExample{
    Find the inverse of 
    \( h(t) = 4t + 6 \).
}{4in}

\myExample{
    Find the inverse of 
    \( s(z) = \frac{1}{z-1} \).
    This is a tricky problem.
    The basic idea is that we get rid of ``ugly fractions'' my multiplying the their denominators.
}{4in}


% \begin{myProblems2}%
%     {Factor the following monomials into prime factors.}%
%     {2in}%
%     %
%     {\( 32x^2 \)}
%     {\( 8 x^3y^2z \)}
% \end{myProblems2}
  


\end{document}