

\begin{myConceptSteps}{\,To solve word problems from geometry $f(x)$\dots}
    \myStep{given}{%
        Write down all the \gap{given} information.
        }
    \myStep{diagram}{Draw a diagram with the given information on it.}
    \myStep{formula}{Find the formula that solves the problem.}
    \myStep{solve}{Solve the problem by \gap{substituting} the given information into the formula.}
\end{myConceptSteps}

Here are some important geometry formulas.

\begin{tcbraster}[colback=white, raster columns=2, raster equal height]
    \begin{tcolorbox}
        {\large\bfseries\itshape rectangle area:} $A = hw$\\
        {\large\bfseries\itshape rectangle perimeter:} $P = 2h + 2w$
        \vspace{1.5in}
    \end{tcolorbox}
    \begin{tcolorbox}
        {\large\bfseries\itshape circle area:} $A = \pi r^2$\\
        \vspace{1.5in}
    \end{tcolorbox}
    \begin{tcolorbox}
        {\large\bfseries\itshape right triangle area:} $A = \frac{1}{2}hw$\\
        \vspace{1.5in}
    \end{tcolorbox}
    \begin{tcolorbox}
        {\large\bfseries\itshape any triangle perimeter:} $P = a + b + c$\\
        \vspace{1.5in}
    \end{tcolorbox}
\end{tcbraster}

\vspace{2em}
\begin{myProblemsWithContent}{2}{Solve these geometry word problems.}
    \begin{tcolorbox}
        The height of a rectangle is $x^2+3$.
        The width of the rectangle is $4x^2 - x - 5$.
        Find a polynomial for the {\bfseries\itshape perimeter} of the rectangle.
        \vspace{4.5in}
    \end{tcolorbox}
    \begin{tcolorbox}
        The base of a right triangle is $x+1$.
        The height of the triangle is $2x-5$.
        Find a polynomial for the {\bfseries\itshape area} of the rectangle.
    \end{tcolorbox}
\end{myProblemsWithContent}

\begin{myProblemsWithContent}{2}{Solve these geometry word problems.}
    \begin{tcolorbox}
        The radius of a circle is $2x + 1$.
        Find a polynomial for the {\bfseries\itshape area} of the circle.
        \vspace{4.5in}
    \end{tcolorbox}
    \begin{tcolorbox}
        The first side of a triangle has a length of  $x^2 + x + 1$.
        The second side of the triangle has a length of $x^2-5$.
        The third side of the triangle has a length of $2x^2 - 2x - 15$.
        Find a polynomial for the {\bfseries\itshape perimeter} of the rectangle.
    \end{tcolorbox}
\end{myProblemsWithContent}

