\emph{Function notation}
is how we write down a function on paper.
It is a precise way to specify
\begin{itemize}
    \item the {\bfseries\itshape name} of the function,
    \item the {\bfseries\itshape rule} that tells you how to calculate the output of the function,
    \item the name of the {\bfseries\itshape input variable}, which is often $x$.
\end{itemize}

\begin{tcolorbox}
The most common notation is $f(x)$.
This tells you that the function is named $f$ 
and that the name of the input variable is $x$.
But it's missing the rule; 
it does not tell us how to calculate the output.

To fully specify a function, including the rule, we write $f(x) = \cdots$,
where the stuff on the right is the rule that says how to calculate the output.
\end{tcolorbox}

In math,
function names are usually (but not always\footnote{
    An example of a function name that is not one letter 
    is $log(x)$, which we will study later in the year.
    In pre-calculus, you will use trigonometric functions,
    $sin(x)$ and $cos(x)$.
    In the software world, function and variable names almost always 
    are words that describe what they do, for example,
    \texttt{send\_email(my\_message)}.
}) a single letter,
and the input variable is often (but not always) $x$.
for example, $f(x)$, $g(z)$, $v(t)$.

\begin{myConceptSteps}{To evaluate a function given the value of its input variable\dots}
    \myStep{substitute}{
        Substitute the value of the input variable wherever it appears in the rule.
        When you substitute, it is a good idea to put \emph{parentheses} around the input value.
    }
    \myStep{evaluate}{Evaluate the expression by using the \emph{order of operations}.}
\end{myConceptSteps}

The words \emph{evaluate} and \emph{simplify} are confusing. 
They mean almost the same thing.
I use the word ``evaluate'' when you should end up with a {\bfseries\itshape number} 
after you apply the order of operations.
I usually use the word ``simplify'' when you should end up with an {\bfseries\itshape expression} with variables in it 
after you apply the order of operations.

\myBlankExample{2in}{
    Given the function
    \(
        f(x) = 3x-5
    \)
    evaluate $f(4)$.
}

\begin{taggedblock}{on-level}
    \myBlankExample{3in}{
        Given the function
        \(
            g(z) = z^2 + 2z + 3
        \)
        evaluate $g(-2)$.
    }
\end{taggedblock}

\myBlankExample{3in}{
    Given the function
    \(
        g(z) = 3z^2 - 2z + 1
    \)
    evaluate $g(-3)$.
}

\begin{taggedblock}{pre-AP}
    \myBlankExample{3in}{
        Given the function
        \(
            v(t) = \frac{1}{2}t^2 + 4t + 3
        \)
        evaluate $f(-4)$.
    }
\end{taggedblock}
