\documentclass[fleqn,letterpaper,12pt,printwatermark=false]{memoir}
% memoir commands to define the text block geometry
\setulmarginsandblock{0.5in}{*}{*}
\setlrmarginsandblock{0.5in}{*}{*}
% put "extra" vertical space at the bottom of a page
\raggedbottom 

\usepackage{amsmath}
\usepackage{xparse} % for NewDocumentCommand et al.
\usepackage{enumitem}
\usepackage{transparent} % for \transparent, which I use in the watermark
\usepackage[slantedGreek]{mathpazo} \usepackage{helvet} % use Palatino et al.
\usepackage{booktabs} % prettier tables

\usepackage[]{xwatermark}
\newwatermark*[
    allpages,
    color=red!30,angle=45,
    scale=4,
    xpos=-10, ypos=0
]{%
    \transparent{0.4}dhasan example%
}

\usepackage{dashundergaps} % for \gap
\dashundergapssetup{
    teacher-mode=true, % set to true to show answers 
    gap-format=underline,
    teacher-gap-format=underline,
    gap-font={\sffamily},
    gap-numbers=true,
    gap-widen=true,
    gap-extend-percent=150, % note: making this too big might create errors
    gap-number-format=\,\textsuperscript{\normalfont(\thegapnumber)},
}

\usepackage{tcolorbox}
\tcbuselibrary{skins}
\tcbuselibrary{raster}

\usepackage{pgfplots}
\pgfplotsset{compat=newest}

% ---------------------DOCUMENT------------------------------
\begin{document}

\newcommand{\myClassName}{Pre-AP Algebra 2}
\newcommand{\myUnitNumber}{1}
\newcommand{\myUnitTitle}{Introduction to Functions}
\newcommand{\myLessonNumber}{10}
\newcommand{\myLessonTitle}{Sketching Inverses}


\input{../defs/guided-notes-defs}
\pagestyle{myPagestyle}

\checkandfixthelayout
\setlist{labelindent=\parindent,leftmargin=*,itemsep=0.025em,label=$\circ$}

% ---------------------LESSON------------------------------
\begin{myNotesHeader}
    \item \myCognitiveVerb{sketch} the graph of the inverse of a function
\end{myNotesHeader}

\begin{myVocabulary}
    \myVocabularyWord{sketch}
        {
            draw something quickly without being perfect
        }
    \myVocabularyWord{inverse functions}
        {
            two functions that ``undo'' each other
        }
\end{myVocabulary}

% ---------------------LESSON------------------------------
\begin{myLesson}
    In lesson 1.9 you learned how to find the inverse $f^{-1}$ 
    for a function $f$.
    It was a lot of ``algebra''.
    The key part of those \emph{algebraic} steps was {\bfseries swapping} 
    the $x$ and $y$ variables. 
    What does that mean \emph{geometrically} (visually)?
    In this lesson, we will graph some inverses to find out.

    You should learn two things:

    \begin{myLessonBox}
        Graphing the inverse of $f$ is really just a matter 
        of figuring out what $f^{-1}$ first. 
        Then you just sketch it.
    \end{myLessonBox}

    \begin{myLessonBox}
        If you visually compare the graph of a function
        to the graph of its inverse,
        you will see that they are \emph{mirror images} (reflections)
        across the diagonal line, $y=x$.
    \end{myLessonBox}
\end{myLesson}

% ---------------------CONCEPT 1------------------------------
\begin{myKeyConcepts}[To sketch the inverse of $f(x)$\dots]
    Follow these steps:
    \setlist{labelindent=\parindent,itemsep=0.4em}
    \begin{enumerate}
        \item Find the inverse function $f^{-1}(x)$ using what you learned in Lesson 1.9.
        \item Sketch the graph of that inverse function 
        (by hand if you know how to graph it or using a graphing calculator or Desmos to help you if you don't).
    \end{enumerate}
\end{myKeyConcepts}

\myExample[1]{
    Sketch the graph of the inverse of
    \( f(x) = 3x \)
}{2.75in}

\myExample[2]{
    Sketch the graph of the inverse of
    \( v(t) = 2t-7 \)
}{2.75in}

\myExample[3]{
    Sketch the graph of the inverse of
    \( f(x) = \frac{2}{5}x- \frac{1}{5} \)
}{2.75in}

% ---------------------CONCEPT 2------------------------------
\begin{myKeyConcepts}[To see the visual relationship between a function and its inverse\dots]
    Follow these steps:
    \setlist{labelindent=\parindent,itemsep=0.4em}
    \begin{enumerate}
        \item Sketch the graph of the original function $y = f(x)$.
        \item Sketch the graph of the inverse function $y = f^{-1}(x)$.
        \item Lightly sketch the graph of the diagonal line, $y=x$ (or draw it as a dotted line).
        \item Notice that the graph of the inverse function 
        is the mirror image (reflection) of the original function 
        across that diagonal line.
    \end{enumerate}
\end{myKeyConcepts}

\begin{myExampleForTikzGraphs}*[4]{
    Let's consider the function 
    \( f(x) = x^5 \).
    It turns out (we will learn this later in the year)
    that the inverse of this function its
    \( f^{-1}(x) = \sqrt[5](x) \).
}
    We could (but you don't need to) use a graphing calculator or Desmos to graph $f$ and $f^{-1}$:

    \begin{center}
    \begin{tikzpicture}
    \begin{axis}[
        width=3in,
        grid=both,
        axis x line = middle,axis y line = middle,
        % axis equal image,
        xtick distance = 1, ytick distance = 1,
        minor tick num=10,
        ]
        \addplot[no marks,densely dotted,thick,domain=-1.1:1.1]{x};
        \addplot[no marks,solid,red,ultra thick,domain=-1:1]{x^3};
        % cube root, see: https://tex.stackexchange.com/questions/69411/pgfplots-cant-plot-some-usual-mathematical-functions
        \addplot[no marks,solid,blue,dashed,ultra thick,domain=-1:1,samples=100]{x/abs(x)*abs(x)^(1/3)};
    \end{axis}
    \end{tikzpicture}
    \end{center}
    
    \noindent Notice how the two graphs are {\bfseries mirror image reflections} of each other 
    across the diagonal line.
\end{myExampleForTikzGraphs}

% \begin{myProblems2}%
%     {Factor the following monomials into prime factors.}%
%     {2in}%
%     %
%     {\( 32x^2 \)}
%     {\( 8 x^3y^2z \)}
% \end{myProblems2}
  


\end{document}